### 2014-11-03 thesis/results/overall-portugal-auc.tex
Fix broken table and figure labels in latex
Lots of changes

\begin{table}[htbp]
\label{tab:overall-pt-auc}
\caption{Overall best AUC of each classifier with a particular feature selection method on the general hospital data set. * indicates that results were identical regardless of discretisation. D indicates that discretisation was used, and $t$ is the threshold at which the feature selector was applied. The absence of * or D means that not discretising produced a better result. The best result for each classifier is highlighted in bold, with ties broken in favour of the smallest feature set.}
\begin{tabular}{|l|cccccc|}
\hline
Classifier & None & CFS & C4.5 Wrapper & Correlation & IG & 1R \\ \hline
ZeroR & 0.5* & 0.5* & 0.5* & 0.5* & 0.5* & 0.5* \\
1R & 0.858* & 0.858* & 0.858* & 0.858* & 0.858* & 0.858* \\
NB & \begin{tabular}[c]{@{}c@{}}0.979\\ D\end{tabular} & 0.982* & \textbf{0.983*} & \begin{tabular}[c]{@{}c@{}}0.981*\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.979*\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.979*\\ t=74.405\end{tabular} \\
DT & \textbf{0.989} & 0.981* & 0.984* & \begin{tabular}[c]{@{}c@{}}0.989\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.989*\\ t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.989*\\ t=74.405\end{tabular} \\
LR & 0.994* & 0.981* & 0.990* & \begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.1\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.05\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.994*\\ t=74.405\end{tabular} \\
SVM & 0.994* & 0.971* & 0.981* & \textbf{\begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.1\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.994*\\ t=74.405\end{tabular} \\
1NN & \begin{tabular}[c]{@{}c@{}}0.979\\ D\end{tabular} & 0.982* & \textbf{0.991*} & \begin{tabular}[c]{@{}c@{}}0.991*\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.990*\\ t=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.989*\\ t=76.905\end{tabular} \\
20NN & 0.992* & 0.981* & 0.991* & \textbf{\begin{tabular}[c]{@{}c@{}}0.992*\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.992*\\ t=0.05\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.992*\\ t=74.405\end{tabular} \\
RD & 0.993* & 0.794* & 0.986* & \textbf{\begin{tabular}[c]{@{}c@{}}0.993*\\ t=0.05\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.993*\\ t=0.005\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.993*\\ t=74.405\end{tabular} \\
K* & 0.994 & 0.980* & 0.989* & \begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.1\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.05\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.994\\ t=74.405\end{tabular} \\
MLP & 0.990* & 0.983* & 0.992* & \textbf{\begin{tabular}[c]{@{}c@{}}0.993*\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.991*\\ t=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.990*\\ t=76.905\end{tabular} \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[htbp]
\begin{tabular}{l|cccccc}
Classifier & None & CFS & C4.5 Wrapper & Correlation & IG & 1R \\ \hline
ZeroR & 0.5* & 0.5* & 0.5* & 0.5* & 0.5* & 0.5* \\
1R & 0.858* & 0.858* & 0.858* & 0.858* & 0.858* & 0.858* \\
NB & \begin{tabular}[c]{@{}c@{}}0.979\\ D\end{tabular} & 0.982* & \textbf{0.983*} & \begin{tabular}[c]{@{}c@{}}0.981*\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.979*\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.979*\\ t=74.405\end{tabular} \\
DT & \textbf{0.989} & 0.981* & 0.984* & \begin{tabular}[c]{@{}c@{}}0.989\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.989*\\ t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.989*\\ t=74.405\end{tabular} \\
LR & 0.994* & 0.981* & 0.990* & \begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.1\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.05\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.994*\\ t=74.405\end{tabular} \\
SVM & 0.994* & 0.971* & 0.981* & \textbf{\begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.1\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.994*\\ t=74.405\end{tabular} \\
1NN & \begin{tabular}[c]{@{}c@{}}0.979\\ D\end{tabular} & 0.982* & \textbf{0.991*} & \begin{tabular}[c]{@{}c@{}}0.991*\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.990*\\ t=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.989*\\ t=76.905\end{tabular} \\
20NN & 0.992* & 0.981* & 0.991* & \textbf{\begin{tabular}[c]{@{}c@{}}0.992*\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.992*\\ t=0.05\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.992*\\ t=74.405\end{tabular} \\
RD & 0.993* & 0.794* & 0.986* & \textbf{\begin{tabular}[c]{@{}c@{}}0.993*\\ t=0.05\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.993*\\ t=0.005\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.993*\\ t=74.405\end{tabular} \\
K* & 0.994 & 0.980* & 0.989* & \begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.1\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.994*\\ t=0.05\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.994\\ t=74.405\end{tabular} \\
MLP & 0.990* & 0.983* & 0.992* & \textbf{\begin{tabular}[c]{@{}c@{}}0.993*\\ t=0.15\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.991*\\ t=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.990*\\ t=76.905\end{tabular} \\
\end{tabular}
\caption{Overall best AUC of each classifier with a particular feature selection method on the general hospital data set. * indicates that results were identical regardless of discretisation. D indicates that discretisation was used, and $t$ is the threshold at which the feature selector was applied. The absence of * or D means that not discretising produced a better result. The best result for each classifier is highlighted in bold, with ties broken in favour of the smallest feature set.}
\label{tab:overall-pt-auc}
\end{table}

### 2014-11-03 thesis/results/overall-trauma-acc.tex
Fix broken table and figure labels in latex
Lots of changes

MLP & \begin{tabular}[c]{@{}c@{}}73.79\\ D\end{tabular} & 73.03* & \begin{tabular}[c]{@{}c@{}}73.45\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.38\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}76.66\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}74.65\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}74.03\\ D, t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}71.94\\ D, t=66.905\end{tabular} \\ \hline

>>>>

MLP & \begin{tabular}[c]{@{}c@{}}73.79\\ D\end{tabular} & 73.03* & \begin{tabular}[c]{@{}c@{}}73.45\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.38\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}76.66\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}74.65\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}74.03\\ D, t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}71.94\\ D, t=66.905\end{tabular} \\

### 2014-11-03 thesis/results/overall-trauma-auc.tex
Fix broken table and figure labels in latex
Lots of changes

MLP & \begin{tabular}[c]{@{}c@{}}0.803\\ D\end{tabular} & 0.781* & \begin{tabular}[c]{@{}c@{}}0.784\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.802\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.825\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.818\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.803\\ D, t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.772\\ D, t=68.905\end{tabular} \\ \hline

>>>>

MLP & \begin{tabular}[c]{@{}c@{}}0.803\\ D\end{tabular} & 0.781* & \begin{tabular}[c]{@{}c@{}}0.784\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.802\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.825\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.818\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.803\\ D, t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.772\\ D, t=68.905\end{tabular} \\

### 2014-11-03 thesis/results/results.tex
Add tables from feature selection
Lots of changes

\section{Overall Performance}
\subsection{Trauma Data Set}
Tables \ref{tab:overall-tr-acc} and \ref{tab:overall-tr-auc} show the best
accuracy and AUC results for each of the feature selection methods for each
classifier. The best accuracy was 77.81\%, achieved using the $k$-NN algorithm
with 1 nearest neighbour, a discretised data set, and feature selection using a
C4.5 wrapper. The best AUC of 0.846 was achieved using logistic regression with
features selected by a correlation coefficient threshold of 0.1, and again
using the discretised data set.

@@

Recall that in order for our work to be comparable to that of previous work on
trauma LOS prediction by Dinh et al. \cite{Dinh2013a}, we use the same data set
that they used, and also tested the features they used as one of the manual
feature selection methods. From Table \ref{tab:overall-tr-acc} we can see that
the best accuracy achieved using their features is 75.06\% with logistic
regression. It is worth noting that our best accuracy, using $k$-NN with 1
nearest neighbour, improves upon the accuracy that they achieved by 2.75\%
while using only 11 features (compared to the 19 they used). These 11 features
make up only 14.1\% of all features in the data set, and performed better than
the 11 features selected manually by the domain expert.

Despite our inclusion of accuracy as an evaluation metric, the AUC is what Dinh
et al. used to evaluate the ability of their logistic regression classifier to
discriminate between the two LOS classes. Using their features, the best AUC
was 0.812 with logistic regression, and our best result was 0.846, also with
logistic regression. However, this was using the discretised data set with 29
features selected by correlation coefficient at a threshold of 0.1.
Although our logistic regression classifier exhibited an AUC improvement of
0.034, it required roughly 50\% more features than the baseline of 19 features.
If we are willing to sacrifice a little discriminating power, we are able to
achieve 0.838 AUC with only 11 features using the K* classifier.

@@

\subsection{General Data Set}
For the general hospital data set, we report the best accuracy and AUC results
for each combination of classifier and feature selection method in Tables
\ref{tab:overall-pt-acc} and \ref{tab:overall-pt-auc}. The most accurate
classifier was the C4.5 decision tree using all 14 features.
This result was the same
regardless of whether or not discretisation was first applied to the data set.
The best AUC result was achieved by three classifiers: logistic regression, SVM
and K*, with an AUC of 0.994. Logistic regression and K* achieved this AUC with
an information gain feature selector with threshold 0.05, and SVM with a
correlation coefficient selector at a 0.1 threshold. We consider logistic
regression and K* to be superior to the SVM in this case because they achieved
the same AUC with only 8 features, whereas the SVM required 10. Being able to
maintain predictive accuracy and the ability to discriminate with less features
means that the classifier is easier to understand. More importantly, we are
able to make a decision with less complete information, a characteristic
which is particularly useful in medicine.

@@

\section{Comparison of Feature Selection Methods}
\subsection{Trauma Data Set}
Tables \ref{tab:features-tr-acc} and \ref{tab:features-tr-auc} show the
best accuracy and AUC achieved with each classifier and feature method, with
both discretised and non-discretised results. We did not include the results of
Zero-R as they do not vary with discretisation or feature selection.
The classifier that achieved the
highest accuracy and AUC over most of the feature selection methods was
logistic regression, with accuracies ranging from 74.4\% with 1R feature
selection to 77.7\% with correlation coefficient feature selection. The AUC
performance of logistic regression ranged from 0.811 to 0.846, again with
1R and correlation feature selection respectively.
\input{results/features-tr-acc.tex}
\input{results/features-tr-auc.tex}

@@

Focussing our attention on the AUC tells a slightly different story. Here we
find that the correlation coefficient and the information gain are the feature
selectors that give the best AUC for most of the classifiers, and perform
equally well when used in conjunction with logistic regression and SVMs.
Interestingly, although the C4.5
wrapper method selects features which allow classifiers to achieve good
accuracy, only in 2 out of the 20 combinations of classifiers did it give the
best AUC result out of all the feature selectors.

@@

\subsection{General Data Set}
Tables \ref{tab:features-pt-acc} and \ref{tab:features-pt-auc} compare the
best accuracy and AUC of each classifier between all the feature selectors
used on the general hospital data set. Again, Zero-R is not included as it
does not vary with discretisation or feature selection. For accuracy, the
best classifier across all feature selectors except CFS was C4.5, and even
then it
was only 0.01\% less accurate than logistic regression and the SVM. Both
logistic regression and SVM achieved 0.994 AUC using no feature selection
as well as correlation, information gain and 1R at the same thresholds. Whereas
in the trauma data set, the MLP did not perform so well compared to many of the
methods, here it produced the best AUC with CFS and C4.5 wrapper feature
selection, resulting in 0.983 and 0.992 AUC respectively.
\input{results/features-pt-acc.tex}
\input{results/features-pt-auc.tex}

@@

\section{Comparison of Classifiers}
\subsection{Trauma Data Set}
Figures \ref{fig:tr-nothreshold} and \ref{fig:tr-threshold} compare the
accuracy and AUC of all classifiers under each feature selection method for
the trauma data set.
The methods that do not select features based upon a specified threshold
(manual methods as well as CFS, C4.5 wrapper and no feature selection)
are graphed in Figure \ref{fig:tr-nothreshold}, and the methods that select
based upon thresholds (correlation, information gain and 1R) are graphed
in Figure \ref{fig:tr-threshold}, showing varying accuracy and AUC as the
threshold is changed.

@@

In terms of classification accuracy, we did not find a lot of variation
between all classifiers, with Zero-R producing 66.91\% accuracy and 77.81\%
being the best we achieved -- an improvement of just over 10\%. The AUC of
the 11 classifiers we tested ranged from 0.498 with Zero-R to 0.846 with
logistic regression. Logistic regression, the \textit{de facto} method
used in LOS classification, performed consistently better than the others
across all feature
selection methods, but only when the feature set was not heavily reduced by
the feature selector: in these cases, such as the results from Figure
\ref{fig:tr-nothreshold-cfs-acc} showing classifier performance with features
selected by CFS, C4.5 decision trees and nearest
neighbour methods have higher accuracy than logistic regression. This is also
apparent from the graphs in Figure \ref{fig:tr-threshold}: for all three
feature selection methods, as we increase the threshold, logistic regression
drops in performance after the initial few thresholds and is outperformed by
C4.5 and the various nearest neighbour classifiers ($k$-NN with 1 and 20
neighbours, Ranked Distance and K*). This is true for both accuracy and AUC.

@@

Nearest neighbour approaches appear to have performed well on this data set in
both accuracy and AUC, especially in comparison to more sophisticated
classifiers and when the feature set is significantly reduced. From the graphs
in Figure \ref{fig:tr-threshold}, we can see that all the nearest neighbours
approaches perform similarly when the number of features is decreased, but our
Ranked Distance approach performs better than the other NN algorithms. This
improvement is not apparent at smaller feature sets, where using the standard
$k$-NN algorithm with 1 or 20 neighbours performs slightly better.
The performance of NN we observed in our results is
an interesting finding because nearest neighbours have not been commonly
applied in predicting the LOS, but there is intuitive appeal in the
case-by-case nature of how these algorithms classify new examples that should
be explored further. Unlike MLPs and SVMs, prediction decision of nearest
neighbours are more transparent and understandable. However, the major drawback
of NN algorithms is their storage requirement and the computational time
required to search for the nearest neighbours to make the classification.

@@

\subsection{General Data Set}
In Figures \ref{fig:pt-nothreshold} and \ref{fig:pt-threshold}, we compare the
performance of the classifiers we used on the general hospital data set. In
contrast to the trauma data, we were able to achieve very high accuracy and
AUC on this data set using the exact same classifiers and feature selection
methods. Instead of only a 10\% improvement from Zero-R by the best classifier
in the trauma data, we were able to achieve an accuracy of 98.23\%, which is
an increase of over 20\% from the Zero-R accuracy on this data set of 75.64\%.
Additionally, we also managed to observe very high ($>0.97$) AUC figures for
all classifiers except Zero-R and 1R.

@@

Notice that in Figure \ref{fig:pt-threshold-corr}, both the accuracy and AUC
of Ranked Distance drop much more than for the other classifiers. This is at
a correlation coefficient threshold of 0.2, which reduces the feature set to
4 features. We noted in the discussion on classifiers for the trauma data set
that Ranked Distance performed worse for smaller feature sets than for larger
ones, and this is another example of this phenomenon. Recall that in Ranked
Distance, features are first ranked according to some similarity metric (we
have used the correlation coefficient), and then assigned a weight according
to their rank. The function we have used assigns rapidly decaying weights to
the features, which results in greater importance being placed on a few of
the features with the highest rank. Further work needs to be carried out to
investigate the cause of the poor performance on smaller feature sets, but
it is not altogether surprising: Ranked Distance performs best by using the
weighted distance contributions of all features, and by significantly reducing
their number we can expect to sharply reduce its ability to differentiate
between neighbours. There is also scope for investigating other weight
assignment functions which would work better in reduced-feature situations.

@@

We found that irrespective of discretisation or feature selection, logistic
regression still performed better than other learning algorithms, which
reaffirms its use as the \textit{de facto} classifier in predictive medicine.
However, we were also able to achieve results that were almost as good using
nearest neighbour approaches combined with feature selection techniques,
neither of which have been investigated thoroughly in previous work. Our
proposed Ranked Distance approach was able to improve the accuracy and AUC of
the standard $k$-NN algorithm with the same number of neighbours, but we found
that its performance suffered when used in conjunction with feature selection.

>>>>

\section{Overall Performance}
\subsection{Trauma Data}
Tables \ref{tab:overall-tr-acc} and \ref{tab:overall-tr-auc} show the best
accuracy and AUC results for each of the feature selection methods for each
classifier. The best accuracy was 77.81\%, achieved using the $k$-NN algorithm
with 1 nearest neighbour, a discretised data set, and feature selection using a
C4.5 wrapper. The best AUC of 0.846 was achieved using logistic regression with
features selected by a correlation coefficient threshold of 0.1, and again
using the discretised data set.

@@

Recall that in order for our work to be comparable to that of previous work on
trauma LOS prediction by Dinh et al. \cite{Dinh2013a}, we use the same data set
that they used, and also tested the features they used as one of the manual
feature selection methods. From Table \ref{tab:overall-tr-acc} we can see that
the best accuracy achieved using their features is 75.06\% with logistic
regression. It is worth noting that our best accuracy, using $k$-NN with 1
nearest neighbour, shows a statistically significant improvement upon the accuracy
that they achieved by 2.75\%
while using only 11 features (compared to the 19 they used). These 11 features
make up only 14.1\% of all features in the data set, and performed better than
the 11 features selected manually by the domain expert. The number of features
selected by each method for each data set is listed in Tables
\ref{tab:features-selected-nothreshold} and
\ref{tab:features-selected-threshold}, and the full details of the selected
features can be found in Appendices \ref{app:features-tr} and
\ref{app:features-pt}.

Despite our inclusion of accuracy as an evaluation metric, the AUC is what Dinh
et al. \cite{Dinh2013a}
used to evaluate the ability of their logistic regression classifier to
discriminate between the two LOS classes. Using their features, the best AUC
was 0.812 with logistic regression, and our best result was 0.846, also with
logistic regression. However, this was using the discretised data set with 29
features selected by correlation coefficient at a threshold of 0.1.
Although our logistic regression classifier exhibited an AUC improvement of
0.034, it required roughly 50\% more features than the baseline of 19 features.
If we are willing to sacrifice a little discriminating power, we are able to
achieve 0.838 AUC with only 11 features using the K* classifier.

@@

\subsection{General Hospital Data}
For the general hospital data set, we report the best accuracy and AUC results
for each combination of classifier and feature selection method in Tables
\ref{tab:overall-pt-acc} and \ref{tab:overall-pt-auc}. The most accurate
classifier was the C4.5 decision tree using all 14 features.
This result was the same
regardless of whether or not discretisation was first applied to the data set.
The best AUC result was achieved by three classifiers: logistic regression, SVM
and K*, with an AUC of 0.994. Logistic regression and K* achieved this AUC with
an information gain feature selector with threshold 0.05, and SVM with a
correlation coefficient selector at a 0.1 threshold. We consider logistic
regression and K* to be superior to the SVM in this case because they achieved
the same AUC with only 8 features, whereas the SVM required 10. Being able to
maintain predictive accuracy and the ability to discriminate with less features
means that the classifier is easier to understand. More importantly, we are
able to make a decision with less complete information, a characteristic
which is particularly useful in medicine.

@@

\section{Comparison of Feature Selection Methods}
\subsection{Trauma Data}
Tables \ref{tab:features-tr-acc} and \ref{tab:features-tr-auc} show the
best accuracy and AUC achieved with each classifier and feature method, with
both discretised and non-discretised results. We did not include the results of
Zero-R as they do not vary with discretisation or feature selection.
The classifier that achieved the
highest accuracy and AUC over most of the feature selection methods was
logistic regression, with accuracies ranging from 74.4\% with 1R feature
selection to 77.7\% with correlation coefficient feature selection. The AUC
performance of logistic regression ranged from 0.811 to 0.846, again with
1R and correlation feature selection respectively.
\input{results/features-tr-acc.tex}
\input{results/features-tr-auc.tex}

@@

\input{results/features-selected-nothreshold.tex}
\input{results/features-selected-threshold.tex}

Focussing our attention on the AUC reveals slightly different patterns. Here we
find that the correlation coefficient and the information gain are the feature
selectors that give the best AUC for most of the classifiers, and perform
equally well when used in conjunction with logistic regression and SVMs.
Interestingly, although the C4.5
wrapper method selects features which allow classifiers to achieve good
accuracy, only in 2 out of the 20 combinations of classifiers did it give the
best AUC result out of all the feature selectors.

@@

\subsection{General Hospital Data}
Tables \ref{tab:features-pt-acc} and \ref{tab:features-pt-auc} compare the
best accuracy and AUC of each classifier between all the feature selectors
used on the general hospital data set. Again, Zero-R is not included as it
does not vary with discretisation or feature selection. For accuracy, the
best classifier across all feature selectors except CFS was C4.5, and even
then it
was only 0.01\% less accurate than logistic regression and the SVM. Both
logistic regression and SVM achieved 0.994 AUC using no feature selection
as well as correlation, information gain and 1R at the same thresholds. Whereas
in the trauma data set, the MLP did not perform so well compared to many of the
methods, here it produced the best AUC with CFS and C4.5 wrapper feature
selection, resulting in 0.983 and 0.992 AUC respectively.
\input{results/features-pt-acc.tex}
\input{results/features-pt-auc.tex}

@@

\section{Comparison of Classifiers}
\subsection{Trauma Data}
Figures \ref{fig:tr-nothreshold} and \ref{fig:tr-threshold} compare the
accuracy and AUC of all classifiers under each feature selection method for
the trauma data set.
The methods that do not select features based upon a specified threshold
(manual methods as well as CFS, C4.5 wrapper and no feature selection)
are graphed in Figure \ref{fig:tr-nothreshold}, and the methods that select
based upon thresholds (correlation, information gain and 1R) are graphed
in Figure \ref{fig:tr-threshold}, showing varying accuracy and AUC as the
threshold is changed.

@@

In terms of classification accuracy, we did not find a lot of variation
between all classifiers, with Zero-R producing 66.91\% accuracy and 77.81\%
being the best we achieved -- an improvement of just over 10\%. The AUC of
the 11 classifiers we tested ranged from 0.498 with Zero-R to 0.846 with
logistic regression. Logistic regression, the \textit{de facto} method
used in LOS classification, performed consistently better than the others
across all feature
selection methods, but only when the feature set was not heavily reduced by
the feature selector: in these cases, such as the results from Figure
\ref{fig:tr-nothreshold-cfs-acc} showing classifier performance with features
selected by CFS, C4.5 decision trees and nearest
neighbour methods have higher accuracy than logistic regression. This is also
apparent from the graphs in Figure \ref{fig:tr-threshold}: for all three
feature selection methods, as we increase the threshold, logistic regression
drops in performance after the initial few thresholds and is outperformed by
C4.5 and the various nearest neighbour classifiers ($k$-NN with 1 and 20
neighbours and K*), as well as our Ranked Distance algorithm.
This is true for both accuracy and AUC.

@@

Nearest neighbour approaches appear to have performed well on this data set in
both accuracy and AUC, especially in comparison to more sophisticated
classifiers and when the feature set is significantly reduced. From the graphs
in Figure \ref{fig:tr-threshold}, we can see that all the nearest neighbours
approaches perform similarly when the number of features is decreased, but our
Ranked Distance algorithm showed a statistically significant improvement over
other NN algorithms. This
improvement is not apparent at smaller feature sets, where using the standard
$k$-NN algorithm with 1 or 20 neighbours performs slightly better.
The performance of NN we observed in our results is
an interesting finding because nearest neighbours have not been commonly
applied in predicting the LOS, but there is intuitive appeal in the
case-by-case nature of how these algorithms classify new examples that should
be explored further. Unlike MLPs and SVMs, prediction decision of nearest
neighbours are more transparent and understandable. However, the major drawback
of NN algorithms is their storage requirement and the computational time
required to search for the nearest neighbours to make the classification.

@@

\subsection{General Hospital Data}
In Figures \ref{fig:pt-nothreshold} and \ref{fig:pt-threshold}, we compare the
performance of the classifiers we used on the general hospital data set. In
contrast to the trauma data, we were able to achieve very high accuracy and
AUC on this data set using the exact same classifiers and feature selection
methods. Instead of only a 10\% improvement from Zero-R by the best classifier
in the trauma data, we were able to achieve an accuracy of 98.23\%, which is
an increase of over 20\% from the Zero-R accuracy on this data set of 75.64\%.
Additionally, we also managed to observe very high ($>0.97$) AUC figures for
all classifiers except Zero-R and 1R.

@@

Notice that in Figure \ref{fig:pt-threshold-corr}, both the accuracy and AUC
of Ranked Distance NN drop much more than for the other classifiers. This is at
a correlation coefficient threshold of 0.2, which reduces the feature set to
4 features. We noted in the discussion on classifiers for the trauma data set
that Ranked Distance NN performed worse for smaller feature sets than for larger
ones, and this is another example of this phenomenon. Recall that in Ranked
Distance NN, features are first ranked according to some similarity metric (we
have used the correlation coefficient), and then assigned a weight according
to their rank. The function we have used assigns rapidly decaying weights to
the features, which results in greater importance being placed on a few of
the features with the highest rank. Further work needs to be carried out to
investigate the cause of the poor performance on smaller feature sets, but
it is not altogether surprising: Ranked Distance NN performs best by using the
weighted distance contributions of all features, and by significantly reducing
their number we can expect to sharply reduce its ability to differentiate
between neighbours. There is also scope for investigating other weight
assignment functions which would work better in reduced-feature situations.

@@

We found that irrespective of discretisation or feature selection, logistic
regression still performed better than other learning algorithms, which
reaffirms its use as the \textit{de facto} classifier in predictive medicine.
However, we were also able to achieve results that were almost as good using
nearest neighbour approaches combined with feature selection techniques,
neither of which have been investigated thoroughly in previous work. Our
proposed Ranked Distance algorithm was able to improve upon the accuracy and AUC of
the standard $k$-NN algorithm with the same number of neighbours, but we found
that its performance suffered when used in conjunction with feature selection.
